Maximum Allowable Current Determination of RBS By Using a Directed Graph Model and Greedy Algorithm

### 2023-11-09 paper/SST/3-main.tex
完成了对 3-main 的全文润色（methodology 部分除外）

% ! NOTE
% 1. red mark -> blue mark
% 2. check ref
% 3. rewrite the last two paragraphs of the introduction if time permits

@@

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
During RBS operation, a critical system parameter known as the maximum allowable current (MAC) become pivotal. This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
By introducing the shortest path of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm into the combination of the shortest paths, which greatly increases the efficiency with which the MAC is determined.
The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated on two published four-battery-RBSs and one with a more complex structure.
The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
The main advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures, even in scenarios with random isolated batteries.
\end{abstract}

%%%%%% Main Text %%%%%%

@@

Battery energy storage systems (BESSs) are extensively used in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, to store and release high-quality electrical energy \cite{choCommercialResearchBattery2015}.
Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required capacity storage.
However, traditional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
Moreover, if the worst battery fails during operation, it is highly likely to exacerbate the degradation of the other batteries, leading to system-level reliability and safety issues \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
These problems have become significant technical barriers in many engineering projects requiring high reliability, such as developing new-generation space vehicles \cite{pomboHybridPowerSystem2021}.  
Reconfigurable battery systems (RBSs), which can dynamically switch as required to different circuit topologies, are expected to solve those problem \cite{hanNextGenerationBatteryManagement2020a}.
In a typical RBS, the extra switches are added between the batteries to form a reconfigurable network, where the circuit's topology can be changed by opening or closing the switches. 
The unhealthy batteries can be isolated from the system by opening the switches adjacent to them, thereby ensuring that the system remains in a reliable working mode \cite{ci2016reconfigurable}. 
Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby improving the system's efficiency and extending the battery's life \cite{bouchhima2018lifetime}. 
Those advantages make RBSs a promising alternative to traditional BESSs.

The early research on RBSs mainly focused on the topological design of the structure with different flexibility and reconfigurability to meet application requirements.
For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to reach the constantly changing voltage requirements during electric vehicle charging.
The structure proposed by Visairo et al. \cite{visairoReconfigurableBatteryPack2008} changes the system's output voltage based on the load conditions, thereby reducing the power loss of the voltage regulator during the power supply process and improving the efficiency of energy use. 
Also, to enhance the energy efficiency of the system, Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
Those complex structures between batteries and switches give RBSs flexibility but also create the challenge in the design of the hardware. 
Current deviation and fluctuation occur when the system is reconfigurating.
Specifically, when the system connect is swithed from series to parallel, circulating current between parallel cells can be triggered due to their voltage imbalance \cite{hanAnalysisEstimationMaximum2020}.
It will bring damage to the batteries, switches, and wires if not fully considered during the design of the RBSs.
For instance, Engelhardt et al. \cite{engelhardtDoubleStringBatterySystem2021} applied the RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while following the voltage request, but the switching of batteries leads to untolerant current variations. 
To solve this problem, Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration. 
This helps guide the selection of switches and supports the design of RBS hardware.

Recently, more attention has been paid to the system state estimation and control of RBSs, and several approaches to optimize the system's performance have been proposed.
The state estimation, one of the essential technologies of the traditional battery management system, is the premise of the system control, and shows great potential in the RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
Couto et al. \cite{coutoPartitionbasedUnscentedKalman2018a} proposed a partition-based unscented Kalman filter to estimate the state of a given large-scale RBS, using an enhanced reduced-order electrochemical model.
Kersten et al. \cite{kerstenOnlineOnBoardBattery2020a} used the balancing current of neighboring cells in parallel operation to determine the battery impedances, yielding state of health and power capability.
Schmid et al. \cite{schmidActiveModelBasedFault2021a} further taken advantage of the system's reconfigured characteristic to actively diagnose fault, whose algorithm changes the structure of the system in order to improve the fault isolability. 
Developing the effective control strategies of RBSs to achieve the optimal performance, such as better stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}, is another hot research topic.
Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the battery charge equalization time.
Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a maximum capacity utilization scheme based on a path planning algorithm to improve the battery consistency within the system.
To break through the bootleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory. 
They thoroughly analyzed all paths between the cathode and anode of each battery in the RBS and identified paths that only contain switches as short-circuit paths for pre-checking before system reconfiguration. 
Furthermore, Artificial Intelligence also appears in the RBS management \cite{liuLongLifetimeBattery2022a}.
The effectiveness of deep reinforcement learning method has been validated on the real-world RBSs \cite{yangAdaptiveControlFramework2022}.

The maximum allowable current (MAC), defined as the maximum allowed current under the constraints of the battery cell, is a critical indicator of RBSs that needs to be evaluated during the design and control of the system. 
The MAC helps the designers assess whether the RBS meets the output current requirements and contributes to the formulation of appropriate and safe management strategies for the battery management system. 
Unfortunately, few studies have been proposed to determine the RBS MAC directly, owing to the complexity from reconfiguration. 
The computer science has the problem of scheduling tasks on dynamically reconfigurable hardware under the condition of limited resources and task interdependencies, similar to the MAC determination, and corresponding solution has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}.
But it is hard to deal with the RBS's structural characteristics and circuit equations. 
From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current in all possible reconfigurations of the RBS. 
However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
Common methods, such as brute-force algorithm, simulated annealing (SA) algorithm and genetic algorithm (GA), have the disadvantages of inefficient, time-consuming, and cannot guarantee to obtain the global optimal solution.

To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
In this method, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
This algorithm transforms the inefficiently searching reconfigurations into the proactively combining of the shortest paths of batteries.
An improved direct graph model that considers the voltage, the internal resistance, the MAC of the battery, and the external load is also introduced to analyze the current of the RBS.
The main contributions of this paper can be summarized as follows:
\begin{itemize}
  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
  \item A greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
  \item An improved directed graph model is introduced to provide a specific method for calculating the MAC of a given structure.
\end{itemize}

The remainder of this paper is organized as follows: 
Section II presents the framework and details of the proposed directed graph model and greedy algorithm. 
Section III discusses a case study that uses the proposed method to determine the MACs of two published four-battery RBSs and one with a more complex structure. 
The calculation results, the algorithm's computational complexity, and scenarios such as battery random isolation are also discussed. 
Finally, the concluding remarks are presented in Section IV.

@@

To further elaborate on the efficiency of our algorithm, we analyze the time complexity of both the brute-force algorithm and the greedy algorithm.
If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute-force algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b)2^{N_s}\bm)$.
The greedy algorithm proposed in this paper requires  that SP be found for each battery, which requires $N_b$ iterations.
Each SP can be obtained by several applications of Dijkstra's algorithms.
Therefore, the total time complexity for calculating all SPs is $O\bm(N_b(N_b+2N_s)\log_{10} N\bm)$.
According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b} N_b^{-1}$ on average.
Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b) 2^{N_b} N_b^{-1} \log_{10} N_b+N_b(N_b+2N_s)\log_{10} N\bm)$.
Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute force algorithm.
Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
This is confirmed by the number of structures required to determine the MAC in the previous section. 
Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
This benefits from two key points:
\begin{enumerate}
    \item[(1)] The SPs guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures. This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency.
    \item[(2)] The bisection method further accelerates this process, reducing the complexity from $2^{N_b}$ to $2^{N_b} N_B^{-1} \log_{10} N_b$.
\end{enumerate}

Furthermore, this approach has the capability to handle RBSs with arbitrary structures, which is another significant advantage of it. 
It is able to correctly calculate the MACs of RBSs with arbitrary structures, even when they have different variant batteries, or even random isolated batteries. 
These results have been validate in the previous subsection.

@@

This paper proposes a pervasive and automated method to efficiently compute the MAC of an RBS.
The method is implemented by a greedy algorithm combined with an improved directed graph model.
Not only does the method provides the same global MAC calculation results as the brute force method, but it also improves the calculation efficiency by 3\,000 to 48\,000 times for three RBS structures in the case study.
Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method, which is mainly because of using the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
The main advantage of this method is its ability to calculate the MAC of RBSs with arbitrary structures.
Even in scenarios with random isolated batteries, the proposed method remains effective.
This method helps to fully tap the current output potential of the RBS, guide the RBS structure design and optimization in the design stage, and assist in evaluating the current-overload risk of the system in practical applications.

>>>>

% ! NOTE
% [DONE]
% 1. red mark -> blue mark
% 2. check ref
% 3. rewrite the last two paragraphs of the introduction if time permits

@@

%%%%%% Abstract %%%%%%
\begin{abstract}
Reconfigurable battery systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure that can be adapted to different battery charging and discharging strategies.
During RBS operation, a critical system parameter known as the maximum allowable current (MAC) become pivotal. This parameter is instrumental in maintaining the current of each individual battery within a safe range and serves as a guiding indicator for the system's reconfiguration, thereby ensuring its safety and reliability.
This paper proposes a method to calculate the MAC of arbitrary RBSs using a greedy algorithm in conjunction with a directed graph model of the RBS.
By introducing the shortest path (SP) of the battery, the greedy algorithm transforms the enumeration of switch states in the brute-force algorithm or variable search without utilizing structures in the heuristic algorithms (simulated annealing and genetic algorithm) into the combination of the shortest paths.
This significantly enhances the efficiency with which the MAC is determined.
The directed graph model, based on the equivalent circuit, provides a specific method for calculating the MAC of a given structure.
The proposed method is validated on two published RBS structures and one with a more complex structure.
The results are the same as those of the brute-force algorithm, but the proposed method significantly improves the computational efficiency ($N_s 2^{N_s - N_b} \log_{10} N_b$ times faster than the brute-force algorithm for an RBS with $N_b$ batteries and $N_s$ switches, theoretically).
Another advantage of the proposed method is its ability to calculate the MAC of RBSs with arbitrary structures and variable battries, even in scenarios with random isolated batteries.
\end{abstract}

@@

Battery energy storage systems (BESSs) are widely utilized in various applications \cite{yangBatteryEnergyStorage2018}, such as wind power plants \cite{desiqueiraControlStrategySmooth2021} and space power systems \cite{schwanbeckInternationalSpaceStation2019,zhangDevelopmentProspectChinese2021}, for the purpose of storing and releasing high-quality electrical energy \cite{choCommercialResearchBattery2015}.
Typically, a BESS consists of numerous batteries interconnected by series-parallel circuitry to provide the required storage capacity.
However, conventional BESSs, in which the batteries are connected in a fixed topology, suffer from a significant weakness in their worst battery due to the so-called cask effect.
Furthermore, if the worst battery fails during operation, it is highly likely to accelerate the degradation of the other batteries, resulting in reliability and safety issues at the system level \cite{yangUnbalancedDischargingAging2016,fengPropagationMechanismsDiagnosis2019,jeevarajanBatterySafetyQualifications2012}.
These challenges have become major technical obstacles in many engineering projects that demand high reliability, such as the development of next-generation space vehicles \cite{pomboHybridPowerSystem2021}.
Reconfigurable battery systems (RBSs), which can dynamically switch between different circuit topologies as needed, are expected to address these issues \cite{hanNextGenerationBatteryManagement2020a}.
In a typical RBS, additional switches are introduced between the batteries to form a reconfigurable network, where the circuit's topology can be altered by opening or closing the switches.
By opening the switches adjacent to the unhealthy batteries, they can be isolated from the system, ensuring that the system remains in a reliable operational state \cite{ci2016reconfigurable}.
Furthermore, the RBS can be reconfigured to adapt to different charging and discharging strategies, thereby enhancing the system's efficiency and prolonging the battery's lifespan \cite{bouchhima2018lifetime}.
These advantages make RBSs a promising alternative to traditional BESSs.

The early research on RBSs mainly focused on the topological design of the structure, incorporating different levels of flexibility and reconfigurability to meet application requirements.
For example, Ci et al. \cite{ci2007novel} proposed an RBS structure that dynamically adjusts the battery discharge rate to fully exploit the available capacity of each battery. 
Jan's \cite{9209774,engelhardt2021double} structures reconfigure circuits with variant batteries in series to accommodate the constantly changing voltage requirements during electric vehicle charging.
The structure proposed by Visairo et al. \cite{visairoReconfigurableBatteryPack2008} alters the system's output voltage based on the load conditions, thereby reducing power loss in the voltage regulator during the power supply process and enhancing energy efficiency. 
Also, to enhance the energy efficiency of the system, Lawson et al. \cite{lawsonSoftwareConfigurableBattery2012} and He et al. \cite{he2014reconfiguration}  proposed simplified structures that have fewer switches than Visairo's design.
Kim et al. \cite{kim2009dynamic} improved the system's ability to recover from battery failures by introducing multiple ports into the structure. 
However, these complex structures between batteries and switches provide flexibility to RBSs while also posing challenges in hardware design. 
During the reconfiguration process, current deviation and fluctuation may occur. Specifically, when the system switches from series to parallel connection, circulating current between parallel cells can be triggered due to voltage imbalance \cite{hanAnalysisEstimationMaximum2020}. Failure to fully consider this issue during the design of RBSs can result in damage to the batteries, switches, and wires. 
For example, Engelhardt et al. \cite{engelhardtDoubleStringBatterySystem2021} applied RBS to a fast-charging scenario with adaptive cell switching, which can balance cell states while adhering to voltage requests. However, the switching of batteries leads to intolerable current variations. 
To address this problem, Han et al. \cite{han2021analysis} derived an analytical expression for the maximum switch current during battery system reconfiguration. This analytical expression aids in the selection of switches and supports the hardware design of RBSs.

Recently, there has been increasing attention given to the estimation and control of the system state of RBSs, and several approaches have been proposed to optimize the performance of the system. 
State estimation, which is an essential technology in traditional battery management systems, serves as the foundation for system control and holds great potential in the context of RBSs \cite{komsiyskaCriticalReviewIntelligent2021}.
Couto et al. \cite{coutoPartitionbasedUnscentedKalman2018a} introduced a partition-based unscented Kalman filter to estimate the state of a large-scale RBS, utilizing an enhanced reduced-order electrochemical model. 
Kersten et al. \cite{kerstenOnlineOnBoardBattery2020a} utilized the balancing current of neighboring cells in parallel operation to determine battery impedances, thereby obtaining information about the state of health and power capability. 
Schmid et al. \cite{schmidActiveModelBasedFault2021a} further leveraged the reconfigurable nature of the system to actively diagnose faults, employing an algorithm that changes the system structure to enhance fault isolability. 
Another active research topic is the development of effective control strategies for RBSs to achieve optimal performance, including improved stability \cite{kacetlDesignAnalysisModular2023b} and efficiency \cite{yangAdaptiveControlFramework2022}.
Han et al. \cite{hanNearFastestBatteryBalancing2019a} proposed a near-fastest battery balancing algorithm to minimize the time required for battery charge equalization.
Liu et al. \cite{liuFlexiblePathPlanningbased2023a} also proposed a scheme for maximizing capacity utilization based on a path planning algorithm, aiming to enhance battery consistency within the system.
To break through the bootleneck of the potential short-circuit paths increase exponentially with the RBS's scale, Chen et al. \cite{chenSneakCircuitTheory2021} proposed a systematic approach based on sneak circuit theory. 
They conducted a comprehensive analysis of all paths between the cathode and anode of each battery in the RBS, identifying paths that only consist of switches as short-circuit paths for pre-checking before system reconfiguration. 
Furthermore, Artificial Intelligence also appears in the RBS management \cite{liuLongLifetimeBattery2022a}.
The effectiveness of deep reinforcement learning method has been validated in real-world RBSs \cite{yangAdaptiveControlFramework2022}.

The maximum allowable current (MAC), which is defined as the maximum current allowed within the constraints of the battery cell, is a crucial indicator of RBSs that needs to be evaluated during the design and control of the system. 
The MAC assists designers in assessing whether the RBS meets the requirements for output current and contributes to the development of appropriate and safe management strategies for the battery management system. 
Unfortunately, there have been few studies proposed to directly determine the MAC of RBSs, primarily due to the complexity arising from reconfiguration. 
In the field of computer science, there is a similar problem of scheduling tasks on dynamically reconfigurable hardware with limited resources and task interdependencies, which is analogous to the determination of MAC. 
A corresponding method has been proposed \cite{mollajafariEfficientLightweightAlgorithm2023,heReconfigurationassistedChargingLargescale2014}. 
However, dealing with the structural characteristics and circuit equations of RBSs is challenging for this method.  
From the perspective of RBS structure analysis, the MAC problem can be transformed into finding the maximum output current among all possible reconfigurations of the RBS. 
However, this may be an NP-hard problem \cite{pinterReviewControlAlgorithms2021a}. 
Common methods such as brute-force algorithms, simulated annealing (SA) algorithms, and genetic algorithms (GA) have the drawbacks of inefficiency, time consumption, and inability to guarantee the globally optimal solution.

To solve this issue, this paper proposes an efficient method to evaluate the MAC of RBSs. 
In this method, a greedy algorithm is designed to efficiently search the possible circuit topology of RBSs with MAC.
This algorithm transforms the inefficiently searching reconfigurations into the proactively combining of the shortest paths of batteries.
Furthermore, an improved directed graph model is introduced to analyze the current of the RBS, taking into account factors such as voltage, internal resistance, MAC of the battery, and external load. 
The main contributions of this study can be summarized as follows:
\begin{itemize}
  \item An efficient method is proposed to determine the MAC of RBSs with arbitrary structures, including scenarios with isolated batteries.
  \item A greedy algorithm is applied to solve the MAC problem, the computational complexity of which is greatly reduced compared with the brute-force algorithm.
  \item An improved directed graph model is introduced to provide a specific method for calculating the MAC of a given structure.
\end{itemize}

The remainder of this paper is organized as follows: 
Section II presents the framework and details of the proposed directed graph model and greedy algorithm. 
Section III examines a case study that applies the proposed method to determine the MACs of two published RBS structures and one with a more complex structure. 
The calculation results, the computational complexity of the algorithm, and scenarios such as battery random isolation are also discussed. 
Finally, the concluding remarks are presented in Section IV.

@@

To further elaborate on the efficiency of our algorithm, we analyze the time complexity of both the brute-force algorithm and the greedy algorithm.
If an RBS has $N_b$ batteries and $N_s$ switches and the corresponding directed graph has $N$ nodes,  $2^{N_s}$ iterations are required to traverse all reconfigured structures.
Calculating each reconfigured structure using Eqs. (\ref{eq:I_o})--(\ref{eq:eta}) requires matrix inversion and matrix multiplication, which has a time complexity of $O(N^3+2N^2N_b+N^2N_s+NN^2_b)$.
Therefore, the time complexity of the brute-force algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b)2^{N_s}\bm)$.
The greedy algorithm proposed in this paper requires  that SP be found for each battery, which requires $N_b$ iterations.
Each SP can be obtained by several applications of Dijkstra's algorithms.
Therefore, the total time complexity for calculating all SPs is $O\bm(N_b(N_b+2N_s)\log_{10} N\bm)$.
According to  Appendix \ref{alg:greedy}, the RBS can reconfigure $C^{N_{\text{set}}}_{N_b}$ structures by selecting $N_{\text{set}}$ batteries from $N_b$ batteries, which gives $\sum^{N_b}_{N_{\text{set}}=1}C^{N_{\text{set}}}_{N_b}/N_b \approx 2^{N_b} N_b^{-1}$ on average.
Thus, with the bisection method, the time complexity of the greedy algorithm is $O\bm((N^3+2N^2N_b+N^2N_s+NN^2_b) 2^{N_b} N_b^{-1} \log_{10} N_b+N_b(N_b+2N_s)\log_{10} N\bm)$.
Based on currently proposed RBS structures \cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711}, the number $N_b$ of batteries, $N_s$ of switches, and $N$ of nodes are quantitatively related as follows: $N_s \approx (3\text{--} 5)N_b$, $N \approx N_s$. 
After simplifying, the time complexity of the method with greedy algorithm is $O(2^{N_b}N_s^2\log_{10} N_b)$, while it is $O(2^{N_s}N_s^3)$ for the method with brute-force algorithm.
Therefore, as the RBS grows, especially in the number of switches, the greedy algorithm gains an advantage over the brute-force algorithm.
This is confirmed by the number of structures required to determine the MAC in the previous section. 
Compared with the brute-force algorithm, the method based on the greedy algorithm is 3\,000 to 48\,000 times more efficient, which is theoretically $N_s 2^{N_s - N_b} \log_{10} N_b$ times according to the above time-complexity analysis.
This benefits from two key points:
\begin{enumerate}
    \item[(1)] The SPs guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures. This reduces the complexity from $2^{N_s}$ to $2^{N_b}$, which is the main reason for the improvement in efficiency. 
    \item[(2)] The bisection method further accelerates this process, reducing the complexity from $2^{N_b}$ to $2^{N_b} N_B^{-1} \log_{10} N_b$.
\end{enumerate}

Furthermore, this approach has the capability to handle RBSs with arbitrary structures, which is another significant advantage of it. 
It is able to correctly calculate the MACs of RBSs with arbitrary structures, even when they have different variant batteries, or even random isolated batteries. 
Theoretically, each RBS structure can be transformed into the unique directed graph model using the methodology described in the Section II, and the MAC can subsequently be calculated using the proposed greedy algorithm.
This finding has been supported in the previous subsection.

@@

This paper proposes a pervasive and automated method to efficiently compute the MAC of an RBS.
The method is implemented by a greedy algorithm combined with an improved directed graph model.
Not only does the method provides the same global MAC calculation results as the brute-force method, but it also demonstrates superior computational efficiency compared to both the brute-force algorithm and the heuristic algorithms (SA and GA). 
Theoretically, for an RBS with $N_s$ switches and $N_b$ batteries, the efficiency of the proposed method is $N_s 2^{N_s - N_b} \log_{10} N_b$ times that of the brute-force method. 
This is primarily due to the utilization of the batteries' SPs to guide the RBS to reconfigure reasonable structures rather than blindly going through all possible structures.
Another advantage of this method is its capability to calculate the MAC of RBSs with arbitrary structures and variant batteries. 
Even in scenarios with random isolated batteries, the proposed method remains effective.
This method facilitates the full utilization of the RBS's current output potential, guides the design and optimization of the RBS structure during the design stage, and assists in evaluating the risk of current overload in practical applications.
